Capstone Movielens Report

### 2025-05-18 reports/capstone-movielens.site/02.5.UME-model.Rmd
RMD report: `User+Movie Effect Model` section completed.

```
```{r}
writeLines("*** The Best Fine-tuning Results ***")
UME.rglr.fine_tune.results$best_result
writeLines("------")
writeLines('')

  print_log1("Re-training Regularized User+Movie Effect Model for the best `lambda`: %1...",
           UME.rglr.best_lambda)
writeLines("------")
writeLines('')

writeLines("*** Regularized User+Movie Effect Structure ***")
str(rglr.UM_effect)
writeLines("------")
writeLines('')
```

@@

RMSEs.ResultTibble.rglr.UME <- RMSEs.ResultTibble.UME |> 
  RMSEs.AddRow("Regularized User+Movie Effect Model", 
               UME.rglr.retrain.RMSE,
               comment = "Computed for `lambda` = %1" |>
                 msg.glue(UME.rglr.best_lambda))
```
```{r}
print_log1("Regularized User+Movie Effect Model has been re-trained for the best `lambda`: %1.",
         UME.rglr.best_lambda)
print_log1("The best RMSE after being regularized: %1",
         UME.rglr.retrain.RMSE)

RMSE_kable(RMSEs.ResultTibble.rglr.UME)
```

>>>>

```
```{r, echo=FALSE}
writeLines("*** The Best Fine-tuning Results ***")
UME.rglr.fine_tune.results$best_result

writeLines("*** Regularized User+Movie Effect Structure ***")
str(rglr.UM_effect)
```

@@

RMSEs.ResultTibble.rglr.UME <- RMSEs.ResultTibble.UME |> 
  RMSEs.AddRow("Regularized User+Movie Effect Model", 
               UME.rglr.retrain.RMSE,
               comment = "Computed for `lambda` = %1" |>
                 msg.glue(UME.rglr.best_lambda))
```
```{r, echo=FALSE}
print_log1("Regularized User+Movie Effect Model has been re-trained for the best `lambda`: %1.",
         UME.rglr.best_lambda)
print_log1("The best RMSE after being regularized: %1",
         UME.rglr.retrain.RMSE)
```
```{r}
RMSE_kable(RMSEs.ResultTibble.rglr.UME)
```
